PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-04-28 paper/ms.tex
add subset of coauthors

%
% key authors:
%
\author[0000-0002-0514-5538]{L.\,G.\,Bouma}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J.\,N.\,Winn}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{TESS collaborators}
\affiliation{ Department of Astrophysical Sciences, Princeton
	University, 4 Ivy Lane, Princeton, NJ 08540, USA}

>>>>

%
% key authors:
%
\author[0000-0002-0514-5538]{L.\,G.\,Bouma}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J.\,N.\,Winn}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%PENDING
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%PENDING
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%PENDING
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%PENDING
\author{S. Seager} % seager@mit.edu
\affiliation{Department of Earth, Atmospheric, and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%
%PENDING
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
% 3 SPOC COAUTHORS
%     Mark E. Rose mark.rose@nasa.gov
%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
%     Bill Wohler  bill.wohler@nasa.gov
% 3 POC COAUTHORS: 
%     John Doty (jpd@noqsi.com)
%     Joel Villaseñor (jsvilla@space.mit.edu)
%     Tom Barclay (barclay.astro@gmail.com)

%PENDING
\author[0000-0001-7139-2724]{T. Barclay} % barclay.astro@gmail.com
\affiliation{NASA Goddard Space Flight Center, 8800 Greenbelt Road,
Greenbelt, MD 20771, USA}
\affiliation{University of Maryland, Baltimore County, 1000 Hilltop
Circle, Baltimore, MD 21250, USA}

%PENDING
\author{J. P. Doty} % jpd@noqsi.com
\affiliation{Noqsi Aerospace Ltd., 15 Blanchard Avenue, Billerica, MA,
01821, USA}

%PENDING
\author[0000-0003-4724-745X]{M. E. Rose} %  mark.rose@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

%PENDING
\author[0000-0002-6148-7903]{J. C. Smith} % jeffrey.c.smith-1@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
\affiliation{SETI Institute, Mountain View, CA 94043, USA}

%PENDING
\author{J. Villase\~nor} % jsvilla@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}

%PENDING
\author[0000-0002-5402-9613]{B. Wohler} % bill.wohler@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
\affiliation{SETI Institute, Mountain View, CA 94043, USA}
